Epistasis is widespread in the genetic control of transcription in humans

### 2013-06-10 docs/manuscript/nature_letter.tex
completed draft of manuscript
Added new data lists for kostya to perform functional annotations on
Updated number of chromosome interactions in manuscript to 44

We also demonstrate a putative novel mechanism by which biological function can lead to epistatic genetic variance. It has been shown that chromosomal regions spatially colocalise in the cell through chromatin interactions \cite{Lieberman-Aiden2009}. We cross referenced our epistatic SNPs with a map of chromosome interacting regions ($n = 96139$) in K562 blood cell lines \cite{Lan2012} and found that fifty epistatic interactions mapped to within 2Mb ($p < 1.8 \times 10^{-10}$), (Supplementary Figure \ref{fig:chromosomeinteractions}), but decyphering the exact cellular processes underlying this interaction requires further research.

@@

>>>>

We also demonstrate a putative novel mechanism by which biological function can lead to epistatic genetic variance. It has been shown that chromosomal regions spatially colocalise in the cell through chromatin interactions \cite{Lieberman-Aiden2009}. We cross referenced our epistatic SNPs with a map of chromosome interacting regions ($n = 96139$) in K562 blood cell lines \cite{Lan2012} and found that 44 epistatic interactions mapped to within 2Mb ($p < 1.8 \times 10^{-10}$), (Supplementary Figure \ref{fig:chromosomeinteractions}), but decyphering the exact cellular processes underlying this interaction requires further research.

@@

\begin{figure}
	\centering
	\includegraphics[width=5in]{alleleFreq}
	\caption{\textbf{Comparison of allele frequencies for 781 SNPs involved in genetic interactions across independent populations} Outliers were removed from the analysis as part of the filtering stage during replication.}
	\label{fig:allelefreq}
\end{figure}
